Differences in care for patients experiencing left vs. right hemisphere ICH

### 2024-02-09 reports/aggressiveness.qmd
shit

library(targets)
library(readr)
library(tidyr)
library(janitor)
library(dplyr)
library(forcats)
library(stringr)
library(skimr)
library(gt)
library(gtsummary)
library(marginaleffects)
library(modelsummary)

tar_load(ich)
tar_load(non_surgery_trials)
tar_load(surgery_trials)
tar_load(table_one)

@@

@@

glimpse(ich)
skim(ich)

@@

## Table 1

@@

Change order of the displayed to frequency

@@

table_one

@@

>>>>

library(targets)
library(readr)
library(tidyr)
library(skimr)
library(dplyr)
library(gt)
library(gtsummary)
library(ggplot2)
library(marginaleffects)
library(modelsummary)

theme_set(theme_minimal(base_family = "Figtree"))

tar_load(ich)
tar_load(non_surgery_trials)
tar_load(surgery_trials)
tar_load(table_1)
tar_load(table_2)

@@

### Data Overview

@@

glimpse(non_surgery_trials)
skim(non_surgery_trials)

@@

### Table 1

@@

Collapse unused levels in `race`, `ethnicity`, `ich_location` and `study`

Change order of the displayed factors to frequency

@@

table_1

@@

### Relationships between Variables

```{r}
#| fig-align: center

table_2

## Statistical Models

::: {.callout-important title="Other Considerations"}

Add analyses stratifying by each study: `ERICH` and `ATACH2`

Construct DAGs for **each** outcome (e.g., each model)!

Add `DNR` in addition to `comfort_care`?

* `neurosurgery_evac`: logistic
* `ventriculostomy`: logistic
* `days_mechanical_ventilation`: poisson (cumulative logit?)
* `tracheostomy`: logistic
* `comfort_care`: logistic (days to comfort care, time to event?)

### DAGs
